Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-08-11 drafts/outline.tex
overleaf

\begin{figure}[htbp]
\includegraphics[width=15cm]{flume.png}
\centering
\caption{Conceptual diagram of the laboratory flume. Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator. Arrows indicate direction of flow. A side view of the open-channel part of the system is included. Dimensions not to scale.}
\label{fig:floorplan}
\end{figure}

@@

Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps, which were placed within the test section in order to estimate the mass of sediment settled due to gravity throughout the flume. To create these sediment traps, the bottom of 50 mL cylindrical plastic syringes were lined flush with microfiber filter paper; the sediment traps were then labelled (A-I) and placed in their respective holes in the test section array before every flume experiment. 
%TODO sed trap paragraph

@@

\begin{figure}[htbp]
\includegraphics[width=15cm,trim = {0 3cm 0 0},clip] {wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.} %TODO get rid of red X's and make a clean, high-res version of figure
\label{fig:sedsize}
\end{figure}

>>>>

\begin{figure}[htbp]
\includegraphics[width=15cm]{flume.png}
\centering
\caption{Conceptual diagram of the laboratory flume. Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator. Arrows indicate direction of flow. A side view of the open-channel part of the system is included. Some dimensions not to scale.}
\label{fig:floorplan}
\end{figure}

@@

Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps, which were spaced uniformly throughout the test section in order to estimate the mass of sediment settled due to gravity. Each trap consisted of a hollow plastic cylinder with a small perforated disk affixed to the inside, on which was placed a glass microfiber filter paper to capture sediment. Nine sediment traps were used, configured in a shape approximating a $3 \times 3$ grid (Figure \ref{fig:floorplan}).

@@

\begin{figure}[htbp]
\includegraphics[width=15cm] {wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.} %TODO get rid of red X's and make a clean, high-res version of figure
\label{fig:sedsize}
\end{figure}
